The SMT Competition 2015--2018

### 2019-03-19 2018/report/SMT-COMP.tex
Add explanation of competitive divisions

Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
highest-ranked solver for each division from 2015--2018.  Entries
$A/B$ indicate that solver~$A$ ranked first considering sequential
performance, while~$B$ ranked first considering parallel performance.
When the same solver ranked first in both, which is most often the
case, its name appears just once.  Some divisions were not
\emph{competitive} (that is, no official winner was declared for
them); we are including all divisions here.  Moreover, we are
including solvers that were running hors concours (and hence
ineligible to be recognized as official competition winners).  Full
division rankings are available from the competition website.

>>>>

Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
highest-ranked solver for each division from 2015--2018.  Entries
$A/B$ indicate that solver~$A$ ranked first considering sequential
performance, while~$B$ ranked first considering parallel performance.
When the same solver ranked first in both, which is most often the
case, its name appears just once.  A division is \emph{competitive} if
at least two substantially different solvers (i.e., solvers from two
different teams) were submitted.  (Experimental divisions are never
competitive.)  Official winners were declared only for competitive
divisions; we are including all divisions here.  Moreover, we are
including solvers that were running hors concours (and hence
ineligible to be recognized as official competition winners).  Full
division rankings are available from the competition website.
